### 2014-09-15 PrivacyProtection-2014-09-09.tex

\subsubsection{IT-Systems \& Humans}

\paragraph{Server Side Mining Scenario (Figure \ref{figure:Live+Gov Operation Scenario 01 - Server Side Mining})}

%\includegraphics{../diagrams/png/scenario01-ServerSideMining.png}
\input{./figures/LG-Operation-Scenario-01-Server-Side-Mining}
\input{./figures/IT-Systems}

The Aggregation Monitor (e) queries the L+G Data Center for aggregated
data. Local Authorities (f) use the Aggregation Monitor to get
information in order to improve public services. \textbf{In this
scenario the mobile the server conducts data mining on aggregated user
data and additionally trys to combine it with publicly accessible data
to enhance the results.}

>>>>

\subsubsection{IT-Systems}

This section outlines the general architecture (Figure \ref{figure:IT Systems}) of IT systems for public monitoring comparable to the Live+Gov project.

\input{./figures/IT-Systems}

\textbf{Description:}
A \textit{Citizen (a)} carries a mobile device running the \textit{Sensor Collector (d)} application.
The \textit{Sensor Collector} application collects sensor data (accelerometer, GPS, GSM, ...) and sends it to the \textit{Data Cetner (c)}. 
The \textit{Data Center} on the other side sends beneficial information (traffic jam reports, bus schedule) for \textit{Citizens} to the mobile device.
The \textit{System Provider (b)} provides and operates technical infrastructure like the Data Center and the \textit{Report Tool (f)}.
The \textit{Report Tool} queries the \textit{Data Center} for aggregated data to visualize in form of charts and other means suitable to help understanding of monitored \textit{Citizens}. 
\textit{Local Authorities (c)} use the \textit{Report Tool} to get information in order to understand citizen movement and improve public services.

In such systems, the most valuable information is not the raw sensor data, the beneficial information for \textit{Local Authorities} is produced via \textit{Data Mining}.

\textbf{In this
scenario the mobile the server conducts data mining on aggregated user
data and additionally trys to combine it with publicly accessible data
to enhance the results.}
